Minimal Positive Influence of Helpline Efforts on Reduction of Homeless Death in Toronto

### 2024-03-12 paper/paper.qmd
rendering issue has been fixed after deleting tbl-subcap

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory model of homeless death count in relation to different helpline efforts"
#| tbl-subcap: "statistical significances are indicated by p < 0.1 *, p < 0.05 **, p < 0.01 ***, p < 0.001"

>>>>

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory model of homeless death count in relation to different helpline efforts"
